Optimal Symmetric Multimodal Templates and Concatenated Random Forests for Supervised Brain Tumor Segmentation (Simplified) with \textit{ANTsR}

### 2014-09-08 Manuscript/template.tex
ENH:  Minor edit.
ENH:  running title.

%\titlerunning{Short form of title}        % if too long for running head

@@

In addition to \textit{R} and the add-on packages previously mentioned, CMake is also 
required.  CMake
%\footnote{
%http://www.cmake.org/
%}
is an open source tool for the management and building of 
large-scale software projects.  It is used
to coordinate the downloading of external packages,
such as the Insight Toolkit (ITK)
%\footnote{
%http://www.itk.org/
%}
and ANTs.  Further instructions for download and
installation can be found on the \textit{ANTsR} github website.  Feel
free to contact the authors if installation trouble occurs.  We note
that \textit{ANTsR} is currently only tested on UNIX-alikes such OSX and Ubuntu
operating systems.
%\footnote{Windows installation should be possible
%but, to our knowledge, has not been attempted.}

@@

>>>>

\titlerunning{Templates, Random Forests, and ANTsR for Brain Tumor Segmentation}        % if too long for running head

@@

In addition to \textit{R} and the add-on packages previously mentioned, CMake is also 
required.  CMake
%\footnote{
%http://www.cmake.org/
%}
is an open source tool for the management and building of 
large-scale software projects.  It is used
to coordinate the downloading of external packages,
such as the Insight Toolkit (ITK)
%\footnote{
%http://www.itk.org/
%}
and ANTs.  Further instructions for download and
installation can be found on the \textit{ANTsR} github website.  Feel
free to contact the authors if installation trouble occurs.  We note
that \textit{ANTsR} is currently only tested on OSX and certain Linux
operating systems.
%\footnote{Windows installation should be possible
%but, to our knowledge, has not been attempted.}

@@

\section*{Information Sharing Statement}

The open source ANTsR package is available as compilable source
code or as a set of binaries from its dedicated github
repository (https://github.com/stnava/ANTsR).  
ANTsR is compatible with R versions 3 and above.
Directions for compilation can be found in the README.md file associated 
with the repository.  Installation from source assumes one has a compiler 
and build environment that can be managed with
the cross platform build tool CMake which is available at http://www.cmake.org.  
The associated scripts written specifically
for the BRATS 2013 challenge are found at https://github.com/ntustison/BRATS2013.
A simple 2-D example is also provided at this location illustrating
both training an RF model and prediction using the previously 
described framework.
